% !TEX root = ../resume.tex

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Data Scientist} % Job title
    {Assistance Publique - Hôpitaux de Paris (AP-HP)} % Organization
    {Paris, France} % Location
    {September 2020 - Present} % Date(s)
    {
        AP-HP is a globally recognised university hospital centre with 39 locations, treating more than ten million patients each year.
        \vspace{4.5mm}
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item I use natural language processing to extract knowledge from the hospital's largely unstructured health data.
        \end{cvitems}
    }


    \cventry
    {Research Intern} % Job title
    {InVivo AI} % Organization
    {Montréal, Canada} % Location
    {May 2019 - December 2019} % Date(s)
    {
        InVivo AI is a Montréal-based and Mila-affiliated startup aiming to bring the power of machine learning to drug discovery.
        \vspace{4.5mm}
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item Worked as a research scientist, designing algorithms able to cope with the dire data scarcity that plagues the field.
          \item Co-wrote multiple research papers, including \linkit{https://arxiv.org/pdf/1905.12131.pdf}{Adaptive Deep Kernel Learning}, a method to extract knowledge from different tasks.
          % on methods aiming to extract knowledge from multiple machine-learning problems at once.
          % \item Optimised in-house machine-learning models with a ten-fold speed increase.
          % \item Developed internal tools to schedule training jobs more efficiently, including a web application front-end.
        \end{cvitems}
    }

    \cventry
    {Junior Consultant} % Job title
    {Ekimetrics} % Organization
    {Paris, France} % Location
    {September 2017 - February 2018} % Date(s)
    {
        Ekimetrics is a French data-driven marketing consultancy and a leader in Europe. Extracted actionable insights from client data, and worked on a research project giving more theoretical groundings to the methodology used in the company.
        % extracting actionable insights from clients' data, but I also worked on a research project aiming to give more theoretical groundings to the methodology used in the company.
    }

    \cventry
    {Research Intern} % Job title
    {IBM Research} % Organization
    {Singapore} % Location
    {May 2017 - August 2017} % Date(s)
    {
        % During five months, I led a research endeavour focusing on destination inference in the Singaporean public transportation network. My work was later published, albeit as part of a larger project.
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item Led a research endeavour focusing on destination inference in the Singaporean public transportation network.
            \item My work was later \link{https://dl.acm.org/doi/10.5555/3306127.3331849}{published at the AAMAS conference} as part of a larger project.
        \end{cvitems}
    }
\end{cventries}
